%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{tnr}
% \usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% force build
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%

\begin{document}

\begin{center}
  \textbf{\Huge Reece Holmdahl} \\ \vspace{1pt}
  \small (651) 260-8698 $|$ \href{mailto:reece@holmdahl.io}{\underline{reece@holmdahl.io}} $|$
  \href{https://linkedin.com/in/reeceholmdahl}{\underline{linkedin.com/in/reeceholmdahl}} $|$
  \href{https://github.com/reecelikesramen}{\underline{github.com/reecelikesramen}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Minnesota}{Minneapolis, MN}
{Bachelor of Science in Computer Science, Minor in Mathematics}{August 2021 -- May 2024}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

%-----------OWC SWE I-----------
\resumeSubheading
{Other World Computing}{Woodstock, IL}
{Software Engineer I}{July 2022 -- August 2023}
\resumeItemListStart
\resumeItem{Designed and implemented a new Salesforce-ERP ETL system processing 10K daily records, reducing synchronization failures by 90\% (from 300 to under 20 daily), and established real-time monitoring dashboards with Kibana.}
\resumeItem{Resolved a critical Work Order Automation system failure within three hours, protecting \$50,000 in daily revenue (5\% of company revenue stream).}
\resumeItem{Elevated code quality in .NET and React projects through strategic implementation of design patterns and packages, measurably improving performance and maintainability.}
\resumeItem{Improved sprint delivery from 80\% to 95\% completion rate over four months.}
\resumeItemListEnd

%-----------OWC SWE INTERN-----------
\resumeSubSubheading
{Software Engineer Intern}{April 2022 -- July 2022}
\resumeItemListStart
\resumeItem{Optimized six major database queries in the RMA processing app, increasing performance by 70\% through analysis, indexing improvements, and parallel processing techniques.}
\resumeItem{Improved application responsiveness in three apps through asynchronous programming and intuitive UI elements, resulting in improved efficiency supported by user feedback.}
\resumeItem{Transitioned older software deployments to CI/CD using Jenkins and Octopus, streamlining DevOps processes, enabling automatic testing, and reducing manual errors.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects and Volunteering}
\resumeSubHeadingListStart

%-----------OPEN WEBUI DESKTOP-----------
\resumeProjectHeading
{\href{https://holmdahl.io/projects/open-webui-desktop/}{\textbf{\underline{Open WebUI Desktop}}} $|$ \emph{Tauri, Svelte, TypeScript, Rust}}{December 2024 -- January 2025}
\resumeItemListStart
\resumeItem{Fulfilled a popular community request by developing a desktop app for Open WebUI.}
\resumeItem{Implemented requested features like the floating chatbar, global hotkey, and companion chat window.}
\resumeItem{Created a novel solution for managing application state in Svelte across windows.}
\resumeItem{Contributed the project back to Open WebUI, with development continuing under their organization.}
\resumeItemListEnd

%-----------WEBTRACER-----------
\resumeProjectHeading
{\href{https://holmdahl.io/projects/webtracer/}{\textbf{\underline{WebTracer}}} $|$ \emph{Rust, React, WebAssembly, wgpu}}{October 2024 -- Present}
\resumeItemListStart
\resumeItem{Implemented a realistic light transport simulation (raytracer) from scratch with minimal packages.}
\resumeItem{Optimized render time by leveraging cache locality, SIMD instructions, and concurrency with Rayon.}
\resumeItem{Provided fast and efficient execution with broad browser support by compiling to WebAssembly.}
\resumeItem{Created a React UI for editing scenes, managing assets, and seeing a live preview of the render.}
\resumeItem{Continuing to improve render time by leveraging GPU computation with wgpu and by implementing the ReSTIR technique.}
\resumeItemListEnd

%-----------HOLMDAHL.IO-----------
\resumeProjectHeading
{\href{https://holmdahl.io/projects/holmdahl.io/}{\textbf{\underline{holmdahl.io}}} $|$ \emph{Hugo, React, Vite, GitHub Actions}}{September 2024 -- October 2024}
\resumeItemListStart
\resumeItem{Designed a responsive portfolio website with static site generation to feature professional projects and articles.}
\resumeItem{Integrated Google Tag Manager and Analytics to gain insights into website usage and optimize user experience.}
\resumeItem{Leveraged GitHub Pages and Actions as a no-cost hosting and CI/CD solution with fast serving speeds.}
\resumeItem{Created a Vite build pipeline to minify, use CDN-served JS packages, and bundle WebAssembly to optimize load time.}
\resumeItem{Contributed a responsive image system to the Hugo project that improved PageSpeed Insights score from 68 to 85 and reduced LCP by 50\% on slow 4G connections.}
\resumeItemListEnd

% %-----------VOYAGER SIGHT-----------
% \resumeProjectHeading
% {\href{https://holmdahl.io/projects/voyagersight/}{\textbf{\underline{VoyagerSight}}} $|$ \emph{Python, LangChain, ChromaDB, Pandas}}{Dates?}
% \resumeItemListStart
% \resumeItem{Conducted an extension study on Nvidia's Voyager to examine how multimodal inputs affect Minecraft LLM agents.}
% \resumeItem{Tested the hypothesis that agents with multimodal perception will play more effectively and display more diverse behavior.}
% \resumeItem{Included POV images as context for each gameplay iteration to provide more variation and information to the LLM.}
% \resumeItemListEnd

%-----------ROBOTICS MENTORSHIP-----------
\resumeProjectHeading
{\textbf{Robotics Mentorship} $|$ \emph{Communication, Leadership, Project Management, Java}}{January 2025 -- Present}
\resumeItemListStart
\resumeItem{Volunteering as a software mentor for the Eagan High School FIRST Robotics Competition (FRC) organization.}
\resumeItem{Providing technical guidance to 8 students, developing their proficiency in Software Engineering principles, Java programming, simulation, and computer vision techniques.}
\resumeItem{Working closely with professionals across many disciplines to help students learn novel skills and achieve complex goals.}
\resumeItemListEnd

% %-----------LEARNPYTORCH.IO-----------
% \resumeProjectHeading
% {\textbf{learnpytorch.io} $|$ \emph{PyTorch, Python, Matplotlib, Google Colab}}{September 2025}
% \resumeItemListStart
% \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
% \resumeItemListEnd

% %-----------OPEN-SOURCE CONTRIBUTION-----------
% \resumeProjectHeading
% {\textbf{Open-source Contribution} $|$ \emph{Python, JavaScript, Rust}}{September 2025 -- Present}
% \resumeItemListStart
% \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
% \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \begin{tabbing}
          \hspace{8em} \= \hspace{10em} \= \kill
          \textbf{Languages:}\> C\#, Go, TypeScript/JavaScript, Ruby, Python, Java, Rust, C/C++ \\
          \textbf{Frameworks:} \> .NET, Gin, Node.js, Rails, FastAPI, React, Svelte, Next.js, Spark, PyTorch, NUnit \\
          \textbf{Developer Tools:} \> AWS, Terraform, Git, GitHub, Datadog, Elasticsearch, Jenkins, Octopus, Docker, Kubernetes, Jira \\
          \textbf{Databases:} \> PostgreSQL, MongoDB, DynamoDB, Redis, Snowflake, Microsoft SQL Server
        \end{tabbing}
    }}
\end{itemize}

%-------------------------------------------
\end{document}